\Huge{Vipassana for Hackers} \\ \large{Paper Two: The Brain} \\ \large\textit{Version 0.2}

### 2019-09-29 paper-two/paper-two.tex
cleaning up network images for paper 2

\todo{insert switching diagram}

@@

@@

\todo{ insert image of ``MRI of DMN'' }
\textit{Magnetic Resonance Image of the areas of the brain in the Default Mode Network.}
http://www.frontiersin.org/Neurotrauma/10.3389/fneur.2013.00016/full

@@

@@

\todo{add image of Approximate location of the OFC on an MRI}

@@

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[width=7.5cm]{images/top-dmn-sn-cen-switching.jpg}
  \caption{The Salience Network consists of the Anterior Cingulate Cortex and the
    Anterior Insular Cortex. It helps switch between the Default Mode Network and the
  Central Executive Network.}
  \label{fig:top-dmn-sn-cen-switching}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/top-dmn.png}
  \end{subfigure}
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/side-dmn.png}
  \end{subfigure}
  \caption{Highlighted: areas of the brain firing when the Default Mode Network is active.}
  \label{fig:dmn}
\end{figure}

@@

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=7.5cm]{images/top-sn.jpg}
  \caption{The Salience Network consists of the Anterior Cingulate Cortex and the
    Anterior Insular Cortex. It helps switch between the Default Mode Network and the
  Central Executive Network.}
  \label{fig:top-sn}
\end{figure}

@@

@@

``Brain\_human\_normal\_inferior\_view'' By Patrick J. Lynch, medical illustrator, CC BY
2.5, https://commons.wikimedia.org/w/index.php?curid=1496648

``Brain\_human\_lateral\_view.svg'' By Patrick J. Lynch, medical illustrator, CC BY
2.5, https://commons.wikimedia.org/w/index.php?curid=1496651
